### 2011-05-06 draft2.tex
term translation, minor fixes

\subsection{$\etrans{}$}
$\etrans{e}$ is a term. The translation is direct.

@@

\begin{eqnarray}
\dtrans{f~x_1 \dots x_n = e} &=& \forall x_1 \dots x_n.\etrans{f~x_1 \dots x_n} = \etrans{e}\\
\dtrans{f~x_1 \dots x_n = \mbox{case } e \mbox{ of } [D_i~\overline{z} \mapsto e_i]} &=& \forall x_1 \dots x_n~(\bigwedge_i (\forall \overline{z}~\etrans{e} = \etrans{D_i~\overline{z}} \to \etrans{f~x_1 \dots x_n} = \etrans{e_i})\\
&& \land \etrans{e} = \bad \to \etrans{f~x_1 \dots x_n} = \bad)\\ 
&& \land \etrans{f~x_1 \dots x_n} = \unr \bigvee_i (\texttt{HD}(e) = D_i) 
\end{eqnarray}

\subsection{$\strans{}$}
$\strans{e \in c}$ is a first-order formula.
\begin{eqnarray}
\strans{e \in \any} &=& true\\
\strans{e \in \{x \mid u \}} &=& \unr \lor (\mbox{CF}(\etrans{e}) \land \etrans{u[e/x]} \neq \bad \land \etrans{u[e/x]} \neq False)\\
\strans{e \in x:c_1 \to c_2}  &=& \forall x_1. \strans{x_1 \in c_1} \to \strans{e~x_1 \in c_2[x_1/x]}
\end{eqnarray}
$False$ is a data constructor here.

Remark: we follow the semantics of the POPL paper but it's a bit restrictive.
e.g. in equation 2 we could use the alternate semantics (namely B1 in the POPL paper) : 
$$\strans{e \in \{x \mid u \}} = \unr \lor (\etrans{u[e/x]} \neq \bad \land \etrans{u[e/x]} \neq False)$$

>>>>

\subsection{$\etrans{}$}
$\etrans{e}$ is a term.

\begin{eqnarray}
\etrans{x} &=& x\\
\etrans{f} &=& f\\
\etrans{e_1~e_2} &=& app(e_1,e_2)\\
\etrans{D} &=& D\\
\etrans{\bad} &=& \bad\\
\etrans{n} &=& n\\

@@

\begin{eqnarray}
\dtrans{f~x_1 \dots x_n = e} &=& \forall x_1 \dots x_n.\etrans{f~x_1 \dots x_n} = \etrans{e}\\
\dtrans{f~x_1 \dots x_n = \mbox{case } e \mbox{ of } [D_i~\overline{z} \mapsto e_i]} &=& \forall x_1 \dots x_n~(\bigwedge_i (\forall \overline{z}~\etrans{e} = \etrans{D_i~\overline{z}} \to \etrans{f~x_1 \dots x_n} = \etrans{e_i})\\
&& \land \etrans{e} = \bad \to \etrans{f~x_1 \dots x_n} = \bad)\\ 
&& \land \etrans{f~x_1 \dots x_n} = \unr \bigvee_i (\texttt{HD}(e) = D_i) \lor e = \bad
\end{eqnarray}

Can't we just put a XOR instead of OR in the last line?

\subsection{$\strans{}$}
$\strans{e \in c}$ is a first-order formula.
\begin{eqnarray}
\strans{e \in \any} &=& true\\
\strans{e \in \{x \mid u \}} &=& e = \unr \lor (\mbox{CF}(\etrans{e}) \land \etrans{u[e/x]} \neq \bad \land \etrans{u[e/x]} \neq False)\\
\strans{e \in x:c_1 \to c_2}  &=& \forall x_1. \strans{x_1 \in c_1} \to \strans{e~x_1 \in c_2[x_1/x]}
\end{eqnarray}
$False$ is a data constructor here.

Remark: we follow the semantics of the POPL paper but it's a bit restrictive.
e.g. in equation 13 we could use the alternate semantics (namely B1 in the POPL paper) : 
$$\strans{e \in \{x \mid u \}} = e = \unr \lor (\etrans{u[e/x]} \neq \bad \land \etrans{u[e/x]} \neq False)$$
